---
title: "W_UP_01"
author: "Zaira Gomez"
date: "fall 2020"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
### Plot boxplots


```{r}


boxplot(pushups~position,data=mydata)
```

## Numerical Descriptive Results


# Numerical results



```{r}
favstats(pushups~position,data=mydata)
```

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
The median,max and the mean seems to be higher then the line player seems like the line  player does less pushups over the skill player for example the median for line is 14.5 and the median for the skill player is 47.5 which is higher then the liner player doing less pushups .The minum pushups skilled player did was 18 and the minimum the liner player did is 6 pushups .The skill players can do more pushups then the line players.
## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the
inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

# Inferential  
  
```{r}
t.test(pushups~position,data=mydata)
```
p=.000009421
If they are the same we have a oddball sample .The odds of getting something like this would be impossible it would never happen .The skill players can do more pushups then the line players .
# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
25% of line  players did as many pushups as the skill players.They are way different and the skill players do a lot more pushups then the line  players .
